My title

### 2024-04-18 paper/paper.qmd
fixed some captions

[^1]: An AWP is a powerful but expensive sniper rifle, capable of killing in one shot to the chest
```{r}
#| label: fig-adr
#| fig-cap: Distribution of ADR
#|  - Distribution of Headshot Percentage
#|  - Number of rounds played
#| echo: false
data |> 
  ggplot(aes(x = adr)) +
  geom_histogram(binwidth = 1) +
  labs(x = "ADR", y = "Number of Players") +
  theme_classic()
```
@fig-hs shows the distribution of headshot percentages. A professional *CS* team typically has 4 riflers and 1 AWPer[^1], where riflers aim for the head to do more damage while AWPers are more likely to aim for the chest since it is a larger area and they will kill in a single shot regardless. This could explain why the players are distributed with a left skew.
```{r}
#| label: fig-hs
#| fig-cap: Distribution of Headshot Percentage
#|  - Number of rounds played
#| echo: false
data |> 
  ggplot(aes(x = hs)) +
  geom_histogram(binwidth = 1) +
  labs(x = "Headshot %", y = "Number of Players") +
  theme_classic()
```
@fig-rounds shows the total number of rounds played.
```{r}
#| label: fig-rounds
#| fig-cap: Distribution of Headshot Percentage
#|  - Number of rounds played
#| echo: false
data |> 
  ggplot(aes(x = rounds)) +
  geom_histogram(binwidth = 1000) +
  labs(x = "Rounds Played", y = "Number of Players") +
  theme_classic()
```

>>>>

[^1]: An AWP is a powerful but expensive sniper rifle, capable of killing in one shot to the chest
```{r}
#| label: fig-adr
#| fig-cap: Distribution of ADR
#| echo: false
data |> 
  ggplot(aes(x = adr)) +
  geom_histogram(binwidth = 1) +
  labs(x = "ADR", y = "Number of Players") +
  theme_classic()
```

@fig-hs shows the distribution of headshot percentages. A professional *CS* team typically has 4 riflers and 1 AWPer[^1], where riflers aim for the head to do more damage while AWPers are more likely to aim for the chest since it is a larger area and they will kill in a single shot regardless. This could explain why the players are distributed with a left skew.
```{r}
#| label: fig-hs
#| fig-cap: Distribution of Headshot Percentage
#| echo: false
data |> 
  ggplot(aes(x = hs)) +
  geom_histogram(binwidth = 1) +
  labs(x = "Headshot %", y = "Number of Players") +
  theme_classic()
```
@fig-rounds shows the total number of rounds played.
```{r}
#| label: fig-rounds
#| fig-cap: Number of rounds played
#| echo: false
data |> 
  ggplot(aes(x = rounds)) +
  geom_histogram(binwidth = 1000) +
  labs(x = "Rounds Played", y = "Number of Players") +
  theme_classic()
```
